%\documentclass[12pt]{scrreprt}
\documentclass[12pt]{report} 

% language may be romanian or english (default is english)
% type may be bachelor or master (default is bachelor)
\usepackage[language=english, type=bachelor]{style}

%\geometry{a4paper,top=2.5cm,left=3cm,right=2.5cm,bottom=2.5cm}
%in style
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}

% Attributes for preventing the overlapping of the text written with monospace font (\texttt)
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}

\specialization{Informatică}	
\title{Distribution of audio-video streams in WebRTC sessions}					   
\author{Haja Florin-Gabriel}											
\supervisor{Lect. dr. Sterca Adrian Ioan}				
				
\maketitle


\newpage
\thispagestyle{empty}
\mbox{}


\newpage
\pagenumbering{roman} 

\cleardoublepage
ABSTRACT
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

\par This thesis is an in-depth study of the communication protocols used by the WebRTC project and the way the audio-video content can be distributed across multiple clients. As people are using the Internet productively more and more, it is crucial to ensure the information is transmitted as fluidly as possible. Since some Internet connection may be limited in bandwidth, it is more difficult to handle video call sessions with many users. 
\par We can opt for using a media server that handles the data delivery for us, or to connect each client with the other, in a mesh topology fashion. When attending a class, for example, we are noticing a broadcasting scenario, as the teacher is providing the content and the students are only looking at it, thus the data can be streamed in one direction, and the mesh topology having no real purpose. Instead of serving all the students at once, we can serve a few, which will forward the stream to others, repeatedly streaming until everyone is able to watch what is the teacher showing. We notice a tree topology. A media server is no longer required, meaning cheaper maintenance costs, but sacrificing the low bandwidth each client is using.


\tableofcontents


\newpage
\pagenumbering{arabic}

\input{chapters/chapter1_introduction}
%\addcontentsline{toc}{chapter}{Introducere}
%\addcontentsline{toc}{chapter}{Introduction}

\input{chapters/chapter2}
%\input{chapters/chapter3}
%\input{chapters/chapter4}

%\input{chapters/chapter6_conclusions}
%\addcontentsline{toc}{chapter}{Concluzii}
%\addcontentsline{toc}{chapter}{Conclusions}

\bibliography{references}

\end{document}
